---
title: "Distribution of socio-economic characteristics using VHLSS 2022 and 2023 data"
author: "Binh Le"
date: "`r Sys.Date()`"
output: pdf_document
urlcolor: blue
geometry: "landscape,left=1cm,right=1cm,top=2cm,bottom=2cm"
---




```{r setup, include=FALSE}
library(formatR)
library(tinytex)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment = FALSE, results = 'hide', fig.align = "center", fig.width = 12)
rm(list = ls())

```


# Modifications needed:
- What is ethnicity? It should be clearer. "HH head is from an ethnic minority" is probably what we need here
- Convert ANnual Income, annual consumption in 1,000 VNs and "Area of Land manageed" in ha (it seems to be in sq. meters?) 
- Add 'Nb of years of education of HH Head' and "Commune has a Plant Protection Staff"
- Recode  "HH head is male" by 'is female'
- I've modified parts of line 488-507 and the table header too
- At the end of the script, generate a dataset with these correlates, and the IDs.



```{r farming_hh_id}

library (haven)
library (tidyverse)

hh_ag_22 <- read.csv ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VHLSS_Household_2022/datasets/Ho_Muc4B11_edited.csv") %>%
  select (c("IDHO", "HOSO", starts_with("MA")))

hh_ag_22$MATINH <- as.character(hh_ag_22$MATINH)
hh_ag_22$MAHUYEN <- as.character(hh_ag_22$MAHUYEN)
hh_ag_22$MAXA <- as.character(hh_ag_22$MAXA)
hh_ag_22$MADIABAN <- as.character(hh_ag_22$MADIABAN)
hh_ag_22$IDHO <- as.character(hh_ag_22$IDHO)
hh_ag_22$HOSO <- as.character(hh_ag_22$HOSO)


hh_ag_22$MATINH <- str_pad(hh_ag_22$MATINH, width = 2, pad = "0")
hh_ag_22$MAHUYEN <- str_pad(hh_ag_22$MAHUYEN, width = 3, pad = "0")
hh_ag_22$MAXA <- str_pad(hh_ag_22$MAXA, width = 5, pad = "0")
hh_ag_22$MADIABAN <- str_pad(hh_ag_22$MADIABAN, width = 3, pad = "0")
hh_ag_22$HOSO <- str_pad(hh_ag_22$HOSO, width = 3, pad = "0")

# hh_ag_22 <- hh_ag_22 %>%
#   mutate (panel = 2022)


unique_hh_ag_22 <- hh_ag_22[!duplicated(hh_ag_22$IDHO), ]


hh_ag_23 <- read.csv("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VHLSS_Household_2023/Final/Muc4B11.csv") %>%
  select (c("IDHO", "HOSO", starts_with("MA"))) 


hh_ag_23$MATINH <- as.character(hh_ag_23$MATINH)
hh_ag_23$MAHUYEN <- as.character(hh_ag_23$MAHUYEN)
hh_ag_23$MAXA <- as.character(hh_ag_23$MAXA)
hh_ag_23$MADIABAN <- as.character(hh_ag_23$MADIABAN)
hh_ag_23$IDHO <- as.character(hh_ag_23$IDHO)
hh_ag_23$HOSO <- as.character(hh_ag_23$HOSO)

hh_ag_23$MATINH <- str_pad(hh_ag_23$MATINH, width = 2, pad = "0")
hh_ag_23$MAHUYEN <- str_pad(hh_ag_23$MAHUYEN, width = 3, pad = "0")
hh_ag_23$MAXA <- str_pad(hh_ag_23$MAXA, width = 5, pad = "0")
hh_ag_23$MADIABAN <- str_pad(hh_ag_23$MADIABAN, width = 3, pad = "0")
hh_ag_23$HOSO <- str_pad(hh_ag_23$HOSO, width = 3, pad = "0")
hh_ag_23$IDHO <- paste0 (hh_ag_23$MAXA, hh_ag_23$MADIABAN, hh_ag_23$HOSO)

# hh_ag_23 <- hh_ag_23 %>%
#   mutate (panel = 2023)


unique_hh_ag_23 <- hh_ag_23[!duplicated(hh_ag_23$IDHO), ]


df_farming <- inner_join (unique_hh_ag_22, unique_hh_ag_23, by = c("IDHO", 
                                             "HOSO",
                                             "MATINH",
                                             "MAHUYEN",
                                             "MAXA",
                                             "MADIABAN"))


```


```{r hh_22 data}


ho_thanhvien_22 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/Ho_ThanhVien.dta") %>%
  select(c(starts_with(c("MA", "IDHO")),  "HOSO", "M1A_C2", "M1A_C3", "M1A_C5", "M2_C1", "M1A_C10", "KYDIEUTRA")) %>%
  group_by(IDHO) %>%
  mutate (n_member = n()) %>%
  rename (c("gender" = "M1A_C2",
            "rls_head" = "M1A_C3", 
            "age" = "M1A_C5",
            "edu_grade" = "M2_C1")) %>%
  filter (rls_head == 1) %>%
  mutate (male = case_when(gender==1 ~ 1,
                           gender==2 ~ 0,
                           TRUE ~ NA)) %>%
  mutate (female = case_when (male == 1 ~ 0,
                              male == 0 ~ 1,
                              TRUE ~ NA)) %>%
  mutate (internet = case_when (M1A_C10 == 1 ~ 1,
                                M1A_C10 == 2 ~ 0,
                                TRUE ~ NA)) %>%
  select (-c("gender", "M1A_C10"))


ho_thanhvien_22$edu_grade[ho_thanhvien_22$edu_grade == 99] <- NA



ho_thongtinho_22 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/Ho_ThongTinHo.dta") %>%
  select(c(starts_with(c("MA", "IDHO")), "HOSO", "DANTOCCHUHO", "THUNHAP", "TONGCHITIEU"))





ho_muc4b0_22 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/ho_muc4b0.dta") %>%
  rename(c("id_land" = "M4B0_MA",
             "land_area" = "M4B0_C3")) %>%
  pivot_wider(names_from = id_land,
              values_from = land_area,
              names_prefix = "land_area_") %>%
  mutate (land_area_sum = rowSums(select(., starts_with("land_area_")), na.rm = TRUE))





ho_thongtinho_22$MATINH <- as.character(ho_thongtinho_22$MATINH)
ho_thongtinho_22$MAHUYEN <- as.character(ho_thongtinho_22$MAHUYEN)
ho_thongtinho_22$MAXA <- as.character(ho_thongtinho_22$MAXA)
ho_thongtinho_22$MADIABAN <- as.character(ho_thongtinho_22$MADIABAN)
ho_thongtinho_22$IDHO <- as.character(ho_thongtinho_22$IDHO)



ho_thanhvien_22$MATINH <- as.character(ho_thanhvien_22$MATINH)
ho_thanhvien_22$MAHUYEN <- as.character(ho_thanhvien_22$MAHUYEN)
ho_thanhvien_22$MAXA <- as.character(ho_thanhvien_22$MAXA)
ho_thanhvien_22$MADIABAN <- as.character(ho_thanhvien_22$MADIABAN)
ho_thanhvien_22$IDHO <- as.character(ho_thanhvien_22$IDHO)




ho_muc4b0_22$MATINH <- as.character(ho_muc4b0_22$MATINH)
ho_muc4b0_22$MAHUYEN <- as.character(ho_muc4b0_22$MAHUYEN)
ho_muc4b0_22$MAXA <- as.character(ho_muc4b0_22$MAXA)
ho_muc4b0_22$MADIABAN <- as.character(ho_muc4b0_22$MADIABAN)
ho_muc4b0_22$IDHO <- as.character(ho_muc4b0_22$IDHO)


hh_df_22 <- full_join (ho_thongtinho_22, ho_thanhvien_22) %>%
  full_join(ho_muc4b0_22) %>%
  group_by (IDHO) 




hh_df_22$MATINH <- str_pad(hh_df_22$MATINH, width = 2, pad = "0")
hh_df_22$MAHUYEN <- str_pad(hh_df_22$MAHUYEN, width = 3, pad = "0")
hh_df_22$MAXA <- str_pad(hh_df_22$MAXA, width = 5, pad = "0")
hh_df_22$MADIABAN <- str_pad(hh_df_22$MADIABAN, width = 3, pad = "0")
hh_df_22$HOSO <- str_pad(hh_df_22$HOSO, width = 3, pad = "0")


hh_df_22$IDHO <- paste0(hh_df_22$MAXA, hh_df_22$MADIABAN, hh_df_22$HOSO)   #hh socio-econs all data


```


```{r commune}
xa_thongtinxa_22 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/Xa_ThongTinXa.dta") %>%
  rename (c("dist_main_str" = "M5C5", 
            "type_main_str" = "M5C7",
            "disease_1" = "M7C1A",
            "disease_2" = "M7C1B",
            "disease_3" = "M7C1C")) %>%
  mutate (poor_commune = case_when (M1C14 ==1 ~ 1,
                                    M1C14 ==2 ~ 0,
                                    TRUE ~ NA),
          dummy_main_str = case_when (M5C4 == 1 ~ 1,
                                      M5C4 == 2 ~ 0,
                                      TRUE ~ NA)) %>%
  select (-c("M1C14", "M5C4")) %>%
  relocate(c("poor_commune", "dummy_main_str"), .before = "dist_main_str") %>%
  select (-"KYDIEUTRA")


xa_muc5a_22 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/Xa_Muc5A.dta") %>%
  rename (c("id_market" = "M5STT1",
            "dist_market" = "M5C25")) %>%
  mutate (dummy_local_market = case_when (M5C24 == 1 ~ 1,
                                          M5C24 == 2 ~ 0,
                                          TRUE ~ NA)) %>%
  select(-"M5C24") %>%
  pivot_wider (names_from = id_market,
               values_from = c("dummy_local_market", "dist_market")) %>%
  rename (c("dummy_local_market_daily" = "dummy_local_market_1",
            "dummy_local_market_periodic" = "dummy_local_market_2",
            "dummy_local_market_wholesale" = "dummy_local_market_3",
            "dist_market_daily" = "dist_market_1",
            "dist_market_periodic" = "dist_market_2",
            "dist_market_wholesale" = "dist_market_3"))  %>%
  select (-"KYDIEUTRA")


xa_muc4c_22 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/Xa_Muc4C.dta") %>%
  rename (c("dist_irrigation" = "M4C27",
            "irrigation_info_1" = "M4C28A",
            "irrigation_info_2" = "M4C28B",
            "irrigation_info_3" = "M4C28C", 
            "farmer_participation_pct" = "M4C29", 
            "ag_challenge_1" = "M4C37A",
            "ag_challenge_2" = "M4C37B",
            "ag_challenge_3" = "M4C37C")) %>%
  select (-c(ends_with("GHIRO"), "M4C33")) %>%
  mutate (dummy_irrigation = case_when (M4C26 ==1 ~ 1,
                                        M4C26 ==2 ~ 0,
                                        TRUE ~ NA),
          dummy_protection_staff = case_when (M4C34 == 1 ~ 1,
                                              M4C34 == 2 ~ 0,
                                              TRUE ~ NA)) %>%
  select (-c("M4C26", "M4C34")) %>%
  relocate ("dummy_irrigation", .before = "dist_irrigation") %>%
  relocate ("dummy_protection_staff", .before = "irrigation_info_1")  %>%
  select (-"KYDIEUTRA")
            
            

xa_thongtinxa_22$MATINH <- as.character(xa_thongtinxa_22$MATINH)
xa_thongtinxa_22$MAHUYEN <- as.character(xa_thongtinxa_22$MAHUYEN)
xa_thongtinxa_22$MAXA <- as.character(xa_thongtinxa_22$MAXA)


xa_muc5a_22$MATINH <- as.character(xa_muc5a_22$MATINH)
xa_muc5a_22$MAHUYEN <- as.character(xa_muc5a_22$MAHUYEN)
xa_muc5a_22$MAXA <- as.character(xa_muc5a_22$MAXA)



xa_muc4c_22$MATINH <- as.character(xa_muc4c_22$MATINH)
xa_muc4c_22$MAHUYEN <- as.character(xa_muc4c_22$MAHUYEN)
xa_muc4c_22$MAXA <- as.character(xa_muc4c_22$MAXA)

commune_df_22 <- full_join (xa_thongtinxa_22, xa_muc5a_22) %>%
  full_join(xa_muc4c_22)
```

```{r merge_df}
hh_commune_df_22 <- left_join(hh_df_22, commune_df_22) 

#Panel 2022

df_22 <- left_join (unique_hh_ag_22, hh_commune_df_22) 

df_22 <- df_22 %>%
  mutate (panel = paste0("2022 (n = ", nrow(df_22), ")"))

# Both panel
data  <- left_join (df_farming, hh_commune_df_22)

data <- data %>%
  mutate (panel = paste0("Both year (n = ", nrow(data), ")"))  #data that in both datasets

```








```{r vh23_prep}
##Uncomment when VH23 is ready:


ho_thanhvien_23 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/Ho_ThanhVien.dta") %>%
  select(c(starts_with(c("MA", "IDHO")),  "HOSO", "M1A_C2", "M1A_C3", "M1A_C5", "M2_C1", "M1A_C10", "KYDIEUTRA")) %>%
  group_by(IDHO) %>%
  mutate (n_member = n()) %>%
  rename (c("gender" = "M1A_C2",
            "rls_head" = "M1A_C3",
            "age" = "M1A_C5",
            "edu_grade" = "M2_C1")) %>%
  filter (rls_head == 1) %>%
  mutate (male = case_when(gender==1 ~ 1,
                           gender==2 ~ 0,
                           TRUE ~ NA)) %>%
  mutate (internet = case_when (M1A_C10 == 1 ~ 1,
                                M1A_C10 == 2 ~ 0,
                                TRUE ~ NA)) %>%
  select (-c("gender", "M1A_C10"))


ho_thanhvien_23$edu_grade[ho_thanhvien_22$edu_grade == 99] <- NA



ho_thongtinho_23 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/Ho_ThongTinHo.dta") %>%
  select(c(starts_with(c("MA", "IDHO")), "HOSO", "DANTOCCHUHO", "THUNHAP", "TONGCHITIEU"))





ho_muc4b0_23 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/ho_muc4b0.dta") %>%
  rename(c("id_land" = "M4B0_MA",
             "land_area" = "M4B0_C3")) %>%
  pivot_wider(names_from = id_land,
              values_from = land_area,
              names_prefix = "land_area_") %>%
  mutate (land_area_sum = rowSums(select(., starts_with("land_area_")), na.rm = TRUE))






ho_thongtinho_23$MATINH <- as.character(ho_thongtinho_23$MATINH)
ho_thongtinho_23$MAHUYEN <- as.character(ho_thongtinho_23$MAHUYEN)
ho_thongtinho_23$MAXA <- as.character(ho_thongtinho_23$MAXA)
ho_thongtinho_23$MADIABAN <- as.character(ho_thongtinho_23$MADIABAN)
ho_thongtinho_23$IDHO <- as.character(ho_thongtinho_23$IDHO)



ho_thanhvien_23$MATINH <- as.character(ho_thanhvien_23$MATINH)
ho_thanhvien_23$MAHUYEN <- as.character(ho_thanhvien_23$MAHUYEN)
ho_thanhvien_23$MAXA <- as.character(ho_thanhvien_23$MAXA)
ho_thanhvien_23$MADIABAN <- as.character(ho_thanhvien_23$MADIABAN)
ho_thanhvien_23$IDHO <- as.character(ho_thanhvien_23$IDHO)




ho_muc4b0_23$MATINH <- as.character(ho_muc4b0_23$MATINH)
ho_muc4b0_23$MAHUYEN <- as.character(ho_muc4b0_23$MAHUYEN)
ho_muc4b0_23$MAXA <- as.character(ho_muc4b0_23$MAXA)
ho_muc4b0_23$MADIABAN <- as.character(ho_muc4b0_23$MADIABAN)
ho_muc4b0_23$IDHO <- as.character(ho_muc4b0_23$IDHO)


hh_df_23 <- full_join (ho_thongtinho_23, ho_thanhvien_23) %>%
  full_join(ho_muc4b0_23) %>%
  group_by (IDHO)




hh_df_23$MATINH <- str_pad(hh_df_23$MATINH, width = 2, pad = "0")
hh_df_23$MAHUYEN <- str_pad(hh_df_23$MAHUYEN, width = 3, pad = "0")
hh_df_23$MAXA <- str_pad(hh_df_23$MAXA, width = 5, pad = "0")
hh_df_23$MADIABAN <- str_pad(hh_df_23$MADIABAN, width = 3, pad = "0")
hh_df_23$HOSO <- str_pad(hh_df_23$HOSO, width = 3, pad = "0")


hh_df_23$IDHO <- paste0(hh_df_23$MAXA, hh_df_23$MADIABAN, hh_df_23$HOSO)   #hh socio-econs all data





xa_thongtinxa_23 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/Xa_ThongTinXa.dta") %>%
  rename (c("dist_main_str" = "M5C5",
            "type_main_str" = "M5C7",
            "disease_1" = "M7C1A",
            "disease_2" = "M7C1B",
            "disease_3" = "M7C1C")) %>%
  mutate (poor_commune = case_when (M1C14 ==1 ~ 1,
                                    M1C14 ==2 ~ 0,
                                    TRUE ~ NA),
          dummy_main_str = case_when (M5C4 == 1 ~ 1,
                                      M5C4 == 2 ~ 0,
                                      TRUE ~ NA)) %>%
  select (-c("M1C14", "M5C4")) %>%
  relocate(c("poor_commune", "dummy_main_str"), .before = "dist_main_str") %>%
  select (-"KYDIEUTRA")


xa_muc5a_23 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/Xa_Muc5A.dta") %>%
  rename (c("id_market" = "M5STT1",
            "dist_market" = "M5C25")) %>%
  mutate (dummy_local_market = case_when (M5C24 == 1 ~ 1,
                                          M5C24 == 2 ~ 0,
                                          TRUE ~ NA)) %>%
  select(-"M5C24") %>%
  pivot_wider (names_from = id_market,
               values_from = c("dummy_local_market", "dist_market")) %>%
  rename (c("dummy_local_market_daily" = "dummy_local_market_1",
            "dummy_local_market_periodic" = "dummy_local_market_2",
            "dummy_local_market_wholesale" = "dummy_local_market_3",
            "dist_market_daily" = "dist_market_1",
            "dist_market_periodic" = "dist_market_2",
            "dist_market_wholesale" = "dist_market_3"))  %>%
  select (-"KYDIEUTRA")


xa_muc4c_23 <- read_dta ("C:/Users/BThanh/SPIA Dropbox/SPIA General/SPIA 2019-2024/5. OBJ.3-Data collection/Country teams/Vietnam/DATA/VH22_Correlates/Xa_Muc4C.dta") %>%
  rename (c("dist_irrigation" = "M4C27",
            "irrigation_info_1" = "M4C28A",
            "irrigation_info_2" = "M4C28B",
            "irrigation_info_3" = "M4C28C",
            "farmer_participation_pct" = "M4C29",
            "ag_challenge_1" = "M4C37A",
            "ag_challenge_2" = "M4C37B",
            "ag_challenge_3" = "M4C37C")) %>%
  select (-c(ends_with("GHIRO"), "M4C33")) %>%
  mutate (dummy_irrigation = case_when (M4C26 ==1 ~ 1,
                                        M4C26 ==2 ~ 0,
                                        TRUE ~ NA),
          dummy_protection_staff = case_when (M4C34 == 1 ~ 1,
                                              M4C34 == 2 ~ 0,
                                              TRUE ~ NA)) %>%
  select (-c("M4C26", "M4C34")) %>%
  relocate ("dummy_irrigation", .before = "dist_irrigation") %>%
  relocate ("dummy_protection_staff", .before = "irrigation_info_1")  %>%
  select (-"KYDIEUTRA")



xa_thongtinxa_23$MATINH <- as.character(xa_thongtinxa_23$MATINH)
xa_thongtinxa_23$MAHUYEN <- as.character(xa_thongtinxa_23$MAHUYEN)
xa_thongtinxa_23$MAXA <- as.character(xa_thongtinxa_23$MAXA)


xa_muc5a_23$MATINH <- as.character(xa_muc5a_23$MATINH)
xa_muc5a_23$MAHUYEN <- as.character(xa_muc5a_23$MAHUYEN)
xa_muc5a_23$MAXA <- as.character(xa_muc5a_23$MAXA)



xa_muc4c_23$MATINH <- as.character(xa_muc4c_23$MATINH)
xa_muc4c_23$MAHUYEN <- as.character(xa_muc4c_23$MAHUYEN)
xa_muc4c_23$MAXA <- as.character(xa_muc4c_23$MAXA)

commune_df_23 <- full_join (xa_thongtinxa_23, xa_muc5a_23) %>%
  full_join(xa_muc4c_23)


hh_commune_df_23 <- left_join(hh_df_23, commune_df_22) 

df_23 <- left_join (unique_hh_ag_23, hh_commune_df_23)


df_23 <- df_23 %>%
  mutate (panel = paste0("2023 (n = ", nrow(df_23), ")"))


### POST-MEETING ###

# Recode distance to wholesale market (in km)
#table (df_23$dist_market_wholesale, df_23$dummy_local_market_wholesale) # NA on distance when inside the commune
#mean (df_23$dist_market_wholesale, na.rm=TRUE) # 16km on average when outside commune
#sum (is.na (df_23$dist_market_wholesale)) # n=732 have market in their commune
#sum (df_23$dist_market_wholesale <0, na.rm=TRUE) # n=522 have negative distances
df_23$dist_market_wholesale [is.na (df_23$dist_market_wholesale)] <- 5
df_23$dist_market_wholesale [df_23$dist_market_wholesale < 0] <- 0


# Recode Main access road is asphalt
#table (df_23$type_main_str)
df_23$type_main_str <- ifelse (df_23$type_main_str == 1, TRUE, FALSE)


# Recode distance to irrigation 
#table (df_23$dist_irrigation, df_23$dummy_irrigation) # NA on distance when inside the commune
#mean (df_23$dist_irrigation, na.rm=TRUE) # 14km on average when outside commune
#sum (is.na (df_23$dist_irrigation)) # n=738 have irrigation in their commune
#sum (df_23$dist_irrigation <0, na.rm=TRUE) # n=522 have negative distances
df_23$dist_irrigation [is.na (df_23$dist_irrigation)] <- 5

# Recode Distance to extension center ???
df_23 <- df_23 [, -c(26,32,33,34,35,36,40)]

rm(list=setdiff(ls(), c("df_22", "df_23", "data")))


```
## 1.1. Descriptive Summary

```{r descriptive}

var_group_stat <- c ("DANTOCCHUHO", 
                "age",
                "edu_grade",
                "n_member",
                "male",
                "internet",
                "THUNHAP",
                "TONGCHITIEU",
                "land_area_sum",
                "poor_commune",
                #"dummy_main_str",
                "type_main_str", 
                #"dummy_local_market_daily",
                #"dummy_local_market_periodic",
                #"dummy_local_market_wholesale",
                #"dist_market_daily",
                #"dist_market_periodic",
                "dist_market_wholesale",
               # "dummy_irrigation",
                "dist_irrigation")

var_name_group_stat <- c ("Household head is ethnic minority", 
                     "Age of household head (in yrs)",
                     "Education of hh head: highest completed grade",
                     "Household size",
                     "% of households with female head",
                     "% of households with internet access",
                     "Annual income (in 1,000 VND)",
                     "Annual consumption (in 1,000 VND)",
                     "Area of land managed or used by hh (in ha)",
                     "Commune is labeled as poor (%)",
                     #"Commune having main access road(%)",
                     "Main access road is asphalt", 
                     #"Commune having daily market (%)",
                     #"Commune having periodic market (%)",
                     #"Commune having wholesale market (%)",
                     #"Distance to daily market (in km)",
                     #"Distance to periodic market (in km)",
                     "Distance to wholesale market (in km)",
                     #"Commune having extension center (%)",
                     "Distance to extension center (in km)")


library (stargazer)
library (knitr)

stat_df_22 <- df_22[var_group_stat]
stat_df_panel <- data[var_group_stat]


stat_table_22 <- stargazer(as.data.frame(stat_df_22), 
                           covariate.labels = var_name_group_stat,
                           summary = TRUE,
                           min.max = FALSE)

stat_table_panel <- stargazer(as.data.frame(stat_df_panel),
                              covariate.labels = var_name_group_stat,
                              summary = TRUE,
                              min.max = FALSE)

```

```{r vh23_stat}

#Uncomment code when VH23 is ready:
stat_df_23 <- df_23[var_group_stat]


stat_table_23 <- stargazer(as.data.frame(stat_df_23),
                           covariate.labels = var_name_group_stat,
                           summary = TRUE,
                           min.max = FALSE)

```

```{r prepare_table, results = 'asis'}

# Trim trailing '\\\\' from each element in stat_table_22_stats
out_22 <- stat_table_22[12:31]

out_panel <- stat_table_panel[12:31]


out_22_trimmed <- gsub("\\\\\\\\ $", "", out_22)



out_panel_trimmed_end <- sub("\\\\\\\\ $", "\\\\", out_panel)
out_panel_trimmed_final <- substring(out_panel_trimmed_end, regexpr("&", out_panel_trimmed_end))

```


```{r vh23_prep_table}
#Uncomment when VH23 is ready

out_23 <- stat_table_23[12:31]



out_23_trimmed <- substring(out_23, regexpr("&", out_23)) 

out_23_final <- gsub("\\\\\\\\ $", "", out_23_trimmed)


table_mid <- paste0(out_22_trimmed, out_23_final, out_panel_trimmed_final)

```


```{r merge_full_table}


# # Combine the trimmed statistics
# table_mid <- paste0(out_22_trimmed, out_panel_trimmed_final)

# Remove trailing whitespace and newlines
table_mid <- gsub("\\s+$", "", table_mid)

# Split the table_mid into lines
table_lines <- strsplit(table_mid, "\\\\ ")

# Add '\\\\' at the end of each line
for (i in 1:length(table_lines)) {
  table_lines[[i]] <- paste(table_lines[[i]], "\\", sep = "")
}

# Combine the lines back into a single string
table_mid_fixed <- paste(table_lines, collapse = " \n")


```




```{r vh23_final_stat_table, results = 'asis'}
#Uncomment when VH23 is ready


header <- header <- "\\begin{table}[!htbp]\n\n           \\centering\n\n           \\caption{Descriptive Statistics of Core Variables (VH22, VH23 and Both Years)}\n\n           \\label{tab:combined_stats}\n\n           \\begin{tabular}{l|ccc|ccc|ccc}\n\n           \\hline \\hline\n\n           Variable & \\multicolumn{3}{c|}{Sample A (VH22)} & \\multicolumn{3}{c|}{Sample B (VH23)} & \\multicolumn{3}{c}{Panel (A-B)} \\\\\n\n           - & N & Mean & Std. Dev. & N & Mean & Std. Dev. & N & Mean & Std. Dev. \\\\\n\n           \\hline"


footer <- "\n\\hline\n\n\\end{tabular}\n\n\\end{table}\n"


# Concatenate the table_mid lines with appropriate spacing
cat(header, table_mid_fixed, footer, "\n")
```






